### 2018-07-04 Thesis/Parts/Data/Data.tex
File cleanup

Metric\footnote{As defined and provided by the SciPy library} & Median title rank & Average title rank & Median abstract rank & Average abstract rank  \\

@@

>>>>

Metric\footnotemark & Median title rank & Average title rank & Median abstract rank & Average abstract rank  \\

@@

\footnotetext{As defined and provided by the SciPy library} 
